Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-05-05 Extra/undergraduate-research-symposium-images.qmd
edits

>>>>

```{r}
sign_type_df <- signbase_full_clean %>% 
  pivot_longer(cols = line:star) %>% 
  filter(value != 0) %>% 
  mutate(sign_type = name) %>% 
  group_by(sign_type) %>% 
  summarise(value = n()) %>% 
  arrange(desc(value))

sign_type_plot <- ggplot(sign_type_df) +
  aes(reorder(sign_type, value), x = sign_type, y = value) +
  geom_col() +
  xlab("Sign type") +
  ylab("Count")+
  coord_flip()

ggsave(sign_type_plot, 
      filename =  "signtype.png",
       bg = "white", w = 3.5)
